systemfit: A Package for Estimating\\ Systems of Simultaneous Equations in \proglang{R}

### 2007-07-04 paper/trunk/JSS/response_B.tex

\subsection{Efficiency and maximum likelihood}
% Section 2.3: Somewhere in this section or (2.1) it should be noted that the efficiency results of
% section 2.1 depend on Sigma being known. And that a full maximum likelihood analysis may be
% superior.

We have noted that the GLS estimator (with known $\Sigma$) is efficient,
but the FGLS estimator (with unknown $\Sigma$)
is only \emph{asymptotically} efficient.
Since the iterated SUR (FGLS) estimator converges to FIML results,
the FIML method is not more efficient than iterated SUR (FGLS).

\subsection{Alternative approach}
% Line 215-219: Alternative approach should be explained more clearly.

We have explained the °alternative approach° more clearly now.

### 2007-07-04 paper/trunk/systemfit_other.tex
explained the SUR approach of LIMDEP's TSCS function (OLS -> WLS -> SUR) more clearly now (suggested by referee B); added answer to referee B that we have done this
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/systemfit@793 591db2bd-e0a0-4d22-8c19-2192dbb7da31

The WLS, SUR, W2SLS and 3SLS parameter estimates are consistent
if the residual covariance matrix is calculated
using the residuals from a first-step OLS or 2SLS estimation.
There exists also an alternative slightly different approach.%
\footnote{
For instance, this approach is applied by
the command °TSCS° of the software LIMDEP that carries out SUR estimations
in which all coefficient vectors are constrained to be equal
\citep{greene06}.
}
This alternative approach uses the residuals of a first-step OLS or 2SLS estimation
to apply a WLS or W2SLS estimation on a second step.
Then, it calculates the residual covariance matrix
from the residuals of the second-step estimation
to estimates the model by SUR or 3SLS in a third step.
If no cross-equation restrictions are imposed,
the parameter estimates of OLS and WLS as well as 2SLS and W2SLS are identical.
Hence, in this case both approaches generate the same results.

>>>>

The WLS, SUR, W2SLS and 3SLS parameter estimates are consistent
if the residual covariance matrix is calculated
using the residuals from a first-step OLS or 2SLS estimation.
There exists also an alternative slightly different approach
that consists of three steps.%
\footnote{
For instance, this approach is applied by
the command °TSCS° of the software LIMDEP that carries out SUR estimations
in which all coefficient vectors are constrained to be equal
\citep{greene06}.
}
In a first step, an OLS or 2SLS estimation is applied to obtain residuals
to calculate a (first-step) residual covariance matrix.
In a second step, the first-step residual covariance matrix
is used to estimate the model by WLS or W2SLS
and new residuals are obtained to calculate
a (second-step) residual covariance matrix.
Finally, in the third step,
the second-step residual covariance matrix is used
to estimate the model by SUR or 3SLS.
If no cross-equation restrictions are imposed,
the parameter estimates of OLS and WLS as well as 2SLS and W2SLS are identical.
Hence, in this case both approaches generate the same results.
